Preliminary Thesis Defence

### 2013-11-21 draft.Rnw
ref intro

\begin{itemize}
\item Additional South African Evidence on Pensions and Child Growth
\item Replication: Surviving Andersonville
\item Risk and Uncertainty in Unique Equilibria in Currency Attacks (MS1998)
\item Bitcoin and Remittances: The Potential of Stupid Phones
\item Blacks-Swan and Dragon-King Events in Microeconomics
\end{itemize}

@@

After this the papers follow, in the order listed above. In the end notes I present a brief discussion of my dissertation, as it stands now, a whole.

>>>>

\begin{itemize}
\item Additional South African Evidence on Pensions and Child Growth
\item Replication: Surviving Andersonville
\item Risk and Uncertainty in Unique Equilibria in Currency Attacks
\item Bitcoin and Remittances: The Potential of Stupid Phones
\item Blacks-Swan and Dragon-King Events in Microeconomics
\end{itemize}

@@

After this the papers follow, in the order listed above. In the end notes (\ref{end-notes}) I present a brief discussion of my dissertation, as it stands now, a whole.

\printbibliography
\end{refsection}
